### 2019-06-05 poster/plots/lqg_mu/plot.tex
complete poster draft

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={10}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=6cm,
                      		  width=7cm,  
                      		  ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.48,0.95)},anchor=north east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Regret}]

>>>>

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={10}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=10cm,  
                      		  %ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.47,0.98)},anchor=north east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Regret}]

### 2019-06-05 poster/plots/lqg_mu_sigma/plot.tex
complete poster draft

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={10}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=10cm,  
                      		  %ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.47,0.98)},anchor=north east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Regret}]

>>>>

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={10}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=7cm,  
                      		  ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.47,0.98)},anchor=north east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Regret}]

### 2019-06-05 poster/plots/mc/plot.tex
complete poster draft

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=7cm,  
                      		  %ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.95,0.05)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Return}]

>>>>

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=10cm,  
                      		  %ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  legend style={thin, draw=gray, at={(0.95,0.05)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Return}]

### 2019-06-05 poster/plots/riverswim/plot_main.tex
complete poster draft

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=7cm,  
                      		  %ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  xtick={0,1000,2000,3000,4000,5000},
							  legend style={thin, draw=gray, at={(0.95,0.32)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Return}]

>>>>

\begin{tikzpicture}[line width=1.5pt, mark size=1.5pt, mark repeat={5}]
    		\begin{groupplot}[cycle list/Dark2-6,
    					group style={
                      		  group name=myplot,
                      		  horizontal sep=2cm,
                      		  group size= 1 by 1},
            				mark list fill={.!75!white},
            				cycle multiindex* list={
                				Dark2-6 \nextlist
                				my marks \nextlist
                				very thick \nextlist},
                      		  height=5cm,
                      		  width=10cm,  
                      		  %ylabel style={yshift=-0.1cm},
                      		  xlabel style={yshift=0.1cm},
                      		  yticklabel style={
        						/pgf/number format/fixed,
        						/pgf/number format/precision=5
							  },
							  xtick={0,1000,2000,3000,4000,5000},
							  legend style={thin, draw=gray, at={(0.95,0.32)},anchor=south east},
                      		  grid=both,
							  grid style={gray!10},   
      						  every tick/.style={gray!60},
                      		  ]
        		\nextgroupplot[title={}, 
        					   xlabel={Episodes},
        					   ylabel={Cumulative Return}]
